---
title: "STAT/MATH 495: Problem Set 07"
author: "Daniel Njoo"
date: "2017-10-24"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    collapsed: false
    smooth_scroll: false
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.width=8, fig.height=4.5, message=FALSE, warning = FALSE
  )
set.seed(76)

# Load packages
library(tidyverse)
library(broom)
library(knitr)

train <- read_csv("data/cs-training.csv") %>% 
  rename(Id = X1)
test <- read_csv("data/cs-test.csv") %>% 
  rename(Id = X1)
submission <- read_csv("data/sampleEntry.csv")
```

Information on the competition can be found [here](https://www.kaggle.com/c/GiveMeSomeCredit/data).

# Collaboration

N/A

# Build binary classifier

Build the binary classifier based on a single predictor variable: `DebtRatio`,
`age`, or `MonthlyIncome`. Justify this choice.

```{r}
findbestpred<-function(pred){
  temp<-as.formula(SeriousDlqin2yrs~pred) 
  glm(temp, data=train, family='binomial') %>% 
    broom::tidy(conf.int=TRUE)
}

findbestpred(train$DebtRatio) #pvalue 2.386904e-05
findbestpred(train$age) #pvalue 0.000000e+00
findbestpred(train$MonthlyIncome) #pvalue 1.185516e-54

```

`MonthlyIncome` appears to be the best predictor out of the 3 predictors, evidenced by the lowest pvalue of 1.185516e-54.

```{r}
train2<-train %>% arrange(MonthlyIncome)
fmod<-bayesglm(as.formula(SeriousDlqin2yrs~MonthlyIncome), data=train2, family="binomial")
```

# ROC curve

Based on the ultimate classifier you choose, plot a corresponding ROC curve.

```{r}
predpr <- predict(fmod,type=c("response"))
roc(predpr,test)

```



# ROC curve for random guessing

Instead of using any predictor information as you did above, switch your
predictions to random guesses and plot the resulting ROC curve.

```{r}

```
