---
title: "STAT/MATH 495: Problem Set 07"
author: "Daniel Njoo"
date: "2017-10-24"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    collapsed: false
    smooth_scroll: false
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.width=8, fig.height=4.5, message=FALSE, warning = FALSE
  )
set.seed(76)

# Load packages
library(tidyverse)
library(broom)
library(knitr)

train <- read_csv("data/cs-training.csv") %>% 
  rename(Id = X1)
test <- read_csv("data/cs-test.csv") %>% 
  rename(Id = X1)
submission <- read_csv("data/sampleEntry.csv")
```

Information on the competition can be found [here](https://www.kaggle.com/c/GiveMeSomeCredit/data).

# Collaboration

Help from [here](https://rudeboybert.github.io/STAT495/quickstart.html)

# Build binary classifier

Build the binary classifier based on a single predictor variable: `DebtRatio`,
`age`, or `MonthlyIncome`. Justify this choice.

```{r}
findbestpred<-function(pred){
  temp<-as.formula(SeriousDlqin2yrs~pred) 
  glm(temp, data=train, family='binomial') %>% 
    broom::tidy(conf.int=TRUE)
}

findbestpred(train$DebtRatio) #pvalue 2.386904e-05
findbestpred(train$age) #pvalue 0.000000e+00 => p-value < 1.185516e-54
findbestpred(train$MonthlyIncome) #pvalue 1.185516e-54

```

`MonthlyIncome` appears to be the best predictor out of the 3 predictors, evidenced by the lowest pvalue of 1.185516e-54.

# ROC curve

Based on the ultimate classifier you choose, plot a corresponding ROC curve.

```{r}
library(ROCR)
profiles_train_augmented <- as.formula(SeriousDlqin2yrs~age) %>% glm(data=train, family='binomial')  %>% 
  broom::augment() %>% 
  as_tibble() %>% 
  mutate(p_hat=1/(1+exp(-.fitted)))

pred <- prediction(predictions = profiles_train_augmented$p_hat, labels = profiles_train_augmented$SeriousDlqin2yrs)
perf <- performance(pred, "tpr","fpr")

#use @ to access slot 'name' of object, view all with slotNames, access one with slot(pred, 'name_of_slot), and sapply(slotNames(pred), function(x) length(slot(pred, x))) to see length of all slots (list of 1)
auc <- as.numeric(performance(pred,"auc")@y.values)
plot(perf, main=paste("Area Under the Curve =", round(auc, 3)))
abline(c(0, 1), lty=2)
```

# ROC curve for random guessing

Instead of using any predictor information as you did above, switch your
predictions to random guesses and plot the resulting ROC curve.

```{r}
trainG <- train %>% mutate(guess=sample(0:1,nrow(train), replace=T))
profiles_train_augmentedG <- as.formula(SeriousDlqin2yrs~guess) %>% glm(data=trainG, family='binomial')  %>%
  broom::augment() %>% 
  as_tibble() %>% 
  mutate(p_hat=1/(1+exp(-.fitted)))

predG <- prediction(predictions = profiles_train_augmentedG$p_hat, labels = profiles_train_augmentedG$SeriousDlqin2yrs)
perfG <- performance(pred, "tpr","fpr")

aucG <- as.numeric(performance(predG,"auc")@y.values)
plot(perfG, main=paste("Area Under the Curve =", round(aucG, 3)))
abline(c(0, 1), lty=2)

```
